---
title: "Vanguard LifeStrategy Funds"
format: html
editor: visual
toc: true
---

```{r}
#| echo: false
#| message: false
#| warning: false

# Load packages
library(tidyquant)
library(tidyverse)
library(alphavantager)
library(pracma)
library(patchwork)  # Optional, for combining plots
# library(arrow)
library(plotly)
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
theme_set(theme_light())
```

```{r}
#| echo: false
#| message: false
#| warning: false
rm(list=ls())
# source(file = './alpha_vantage.py')
# ETF <- tq_get(c("VASIX","VSCGX","VSMGX","VSMGX"), get = "alphavantage", av_fun = "TIME_SERIES_DAILY", from = as.Date(format(Sys.Date(), "%Y-01-01"))) |> rename(date = timestamp)


```
```{r}
#| echo: false
#| message: false
#| warning: false
# ETF <- tq_get(c("VASIX","VSCGX","VSMGX","VSMGX"), get = "alphavantage", av_fun = "TIME_SERIES_DAILY") |> rename(date = timestamp)

```

```{r}
ETF <- tq_get(c("VASIX","VSCGX","VSMGX","VASGX")) |> filter(date >='2025-01-01')
max(ETF$date)
```
```{r}
vasix <- ETF |> filter(symbol =='VASIX') 
vscgx <- ETF |> filter(symbol =='VSCGX')
vsmgx <- ETF |> filter(symbol =='VSMGX')
vasgx <- ETF |> filter(symbol =='VASGX')
```
```{r}
etf_div <- tq_get(c("VASIX","VSCGX","VSMGX","VASGX"),get="dividends")
```

## LifeStrategy Income Fund(VASIX)

You may be interested in this fund if you care mostly about current income and accept the limited growth potential that comes with less exposure to stock market risk.

### Close + 100 Day Moving Average

```{r}
vasix$rolling_100d <- movavg(vasix$close,100,type=c("s"))
ggplot(vasix) + geom_line(aes(x=date,y=close,colour="Close"),linewidth=1) +
  geom_line(aes(x=date,y=rolling_100d,colour="50d Rolling"),linewidth=1) +
  theme_tq() + labs(title="VASIX Closng Prices w/ 100 day MA")
  
```

### Bollinger Bands

```{r}
vasix_bb <- vasix %>%
  tq_mutate(select = close, mutate_fun = BBands) |> na.omit()

ggplot(vasix_bb, aes(x = date)) +
  geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightblue", alpha = 0.3) +
  geom_line(aes(y = close), color = "blue", linewidth= 0.8) +
  geom_line(aes(y = up), color = "red", linetype = "dashed") +
  geom_line(aes(y = dn), color = "red", linetype = "dashed") +
  geom_line(aes(y = mavg), color = "darkgreen", linetype = "dotdash") +
  labs(title = "VASIX  - Bollinger Bands (YTD)", x = "Date", y = "Closing Price") +
  theme_tq()

```

### Dividend

```{r}
vasix_div <- etf_div |> filter(symbol=='VASIX')
round(mean(vasix_div$value),3)
ggplot(vasix_div) + geom_col(aes(x=date,y=value))
# ggplotly(bnd_plt) + labs(title="VASIX Dividend")

```

## LifeStrategy Conservative Growth Fund(VSCGX)

You may be interested in this fund if you care about current income more than long-term growth, but still want some growth potential with less exposure to stock market risk.

### Close + 100 Day Moving Average

```{r}
vscgx$rolling_100d <- movavg(vscgx$close,100,type=c("s"))
ggplot(vscgx) + geom_line(aes(x=date,y=close,colour="Close"),linewidth=1) +
  geom_line(aes(x=date,y=rolling_100d,colour="50d Rolling"),linewidth=1) +
  theme_tq() + labs(title="vscgx Closng Prices w/ 100 day MA")
  
```

### Bollinger Bands

```{r}
vscgx_bb <- vscgx %>%
  tq_mutate(select = close, mutate_fun = BBands) |> na.omit()

ggplot(vscgx_bb, aes(x = date)) +
  geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightblue", alpha = 0.3) +
  geom_line(aes(y = close), color = "blue", linewidth= 0.8) +
  geom_line(aes(y = up), color = "red", linetype = "dashed") +
  geom_line(aes(y = dn), color = "red", linetype = "dashed") +
  geom_line(aes(y = mavg), color = "darkgreen", linetype = "dotdash") +
  labs(title = "vscgx - Bollinger Bands (YTD)", x = "Date", y = "Closing Price") +
  theme_tq()

```



```{r}
vscgx_div <- etf_div |> filter(symbol=='VSCGX')
round(mean(vscgx_div$value),3)
ggplot(vscgx_div) + geom_col(aes(x=date,y=value))
# ggplotly(bnd_plt) + labs(title="VASIX Dividend")

```

## LifeStrategy Moderate Growth Fund(VSMGX)

You may be interested in this fund if you care about long-term growth more than current income and want more growth potential while accepting higher exposure to stock market risk.

### Close + 100 Day Moving Average

```{r}
vsmgx$rolling_100d <- movavg(vsmgx$close,100,type=c("s"))
ggplot(vsmgx) + geom_line(aes(x=date,y=close,colour="Close"),linewidth=1) +
  geom_line(aes(x=date,y=rolling_100d,colour="50d Rolling"),linewidth=1) +
  theme_tq() + labs(title="VASGX Closng Prices w/ 100 day MA")
  
```

### Bollinger Bands

```{r}
vsmgx_bb <- vsmgx %>%
  tq_mutate(select = close, mutate_fun = BBands) |> na.omit()

ggplot(vsmgx_bb, aes(x = date)) +
  geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightblue", alpha = 0.3) +
  geom_line(aes(y = close), color = "blue", linewidth= 0.8) +
  geom_line(aes(y = up), color = "red", linetype = "dashed") +
  geom_line(aes(y = dn), color = "red", linetype = "dashed") +
  geom_line(aes(y = mavg), color = "darkgreen", linetype = "dotdash") +
  labs(title = "vsmgx - Bollinger Bands (YTD)", x = "Date", y = "Closing Price") +
  theme_tq()

```

### Dividend

```{r}
vsmgx_div <- etf_div |> filter(symbol=='VSMGX')
round(mean(vsmgx_div$value),3)
ggplot(vsmgx_div) + geom_col(aes(x=date,y=value))

```

## LifeStrategy Growth Fund(VASGX)

You may be interested in this fund if you care about long-term growth and are willing to accept significant exposure to stock market risk in exchange for more growth potential.


### Close + 100 Day Moving Average

```{r}
vasgx$rolling_100d <- movavg(vasgx$close,100,type=c("s"))
ggplot(vasgx) + geom_line(aes(x=date,y=close,colour="Close"),linewidth=1) +
  geom_line(aes(x=date,y=rolling_100d,colour="50d Rolling"),linewidth=1) +
  theme_tq() + labs(title="VASGX Closng Prices w/ 100 day MA")
  
```

### Bollinger Bands

```{r}
vasgx_bb <- vasgx %>%
  tq_mutate(select = close, mutate_fun = BBands) |> na.omit()

ggplot(vasgx_bb, aes(x = date)) +
  geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightblue", alpha = 0.3) +
  geom_line(aes(y = close), color = "blue", linewidth= 0.8) +
  geom_line(aes(y = up), color = "red", linetype = "dashed") +
  geom_line(aes(y = dn), color = "red", linetype = "dashed") +
  geom_line(aes(y = mavg), color = "darkgreen", linetype = "dotdash") +
  labs(title = "vsmgx - Bollinger Bands (YTD)", x = "Date", y = "Closing Price") +
  theme_tq()

```

### Dividend

```{r}
vasgx_div <- etf_div |> filter(symbol=='VASGX')
round(mean(vasgx_div$value),3)
ggplot(vasgx_div) + geom_col(aes(x=date,y=value))

```