---
title: "Vanguard Total International Bond (BNDX) ETF"
subtitle: "W/ tidyquant"
date: '2025-04-25'
format: pdf
toc: true
echo: false
---

```{r}
#| echo: false
#| message: false
#| warning: false

library(tidyquant)
library(tidyverse)
# library(alphavantager)
library(pracma)
# library(patchwork)  # Optional, for combining plots
# library(arrow)
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
theme_set(theme_light())
```

# Summary:

Vanguard’s BNDX fund is designed to give U.S. investors broad exposure to high-quality international bonds while minimizing currency risk through hedging. Its core purpose is to enhance portfolio diversification with global bonds without exposing investors to unpredictable foreign exchange fluctuations.

```{r}
rm(list=ls())
funds <- tq_get("BNDX",from="2025-01-01") 
funds$MA_50d <- movavg(funds$close,50,'s')
max(funds$date)
```

# Closing Price w/ 50 Day Moving Average

```{r}
funds |> filter(date >="2025-02-01") |>
ggplot() + geom_line(aes(x=date,y=close,colour="Close"),linewidth=1) +
  geom_line(aes(x=date,y=MA_50d,colour="50 day MA"),linewidth=1) +
  labs(title="BNDX Close w/ 50 Day Moving Avearge")
 


```

# TQ Bar chart

```{r}

funds %>% filter(date >="2025-02-01") |>
    ggplot(aes(x = date, y = close)) +
    geom_barchart(aes(open = open, high = high, low = low, close = close)) +
    geom_ma(color = "darkgreen") 

```

# Bollinger Bands

```{r}
bnd_bb <- funds %>% filter(date >="2025-02-01") |>
  tq_mutate(select = close, mutate_fun = BBands) |> na.omit()

ggplot(bnd_bb, aes(x = date)) +
  geom_ribbon(aes(ymin = dn, ymax = up), fill = "lightblue", alpha = 0.3) +
  geom_line(aes(y = close), color = "blue", linewidth= 0.8) +
  geom_line(aes(y = up), color = "red", linetype = "dashed") +
  geom_line(aes(y = dn), color = "red", linetype = "dashed") +
  geom_line(aes(y = mavg), color = "darkgreen", linetype = "dotdash") +
  labs(title = "BNDX ETF - Bollinger Bands (YTD)", x = "Date", y = "Closing Price") +
  theme_tq()

```

# Candlesticks

```{r}

funds |> filter(date >="2025-02-01") |> ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close)) +
    geom_ma(color = "darkgreen")
```
